Associahedra for finite type cluster algebras \\ and minimal relations between $\b{g}$-vectors

### 2019-06-13 thirdPaper/draft/typeConeAssociahedra.tex
typographic changes

\begin{proposition}
\label{prop::free-set}
\begin{enumerate}
\item The set~$\set{[\ell_A]}{A \in \ind(\cat) \ssm \add(\susp T)} \cup \set{[\susp T_i]}{i=1, \dots, n}$ is free in~$\Ksp(\cat)$.
\item The set~$\set{[r_A]}{A \in \ind(\cat) \ssm \add(\susp T)} \cup \set{[\susp T_i]}{i=1, \dots, n}$ is free in~$\Ksp(\cat)$.
\end{enumerate}
\end{proposition}

\begin{proof}
We only prove (1); the proof of (2) is similar. Assume that~
\[
x= \sum_{A \in \ind(\cat) \ssm \add(\susp T)} \lambda_A \ell_A + \sum_{i=1}^n \lambda_i [\susp T_i] = 0.
\]
Then~$\langle x, [A] \rangle = 0$ for all~$A\in\ind(\cat) \ssm \add(\susp T)$. But~$\langle x, [A] \rangle = \lambda_A$ by \cref{lemm::bilinear-form}. Thus~
\[
x = \sum_{i=1}^n \lambda_i [\susp T_i] = 0.
\]
But the~$[\susp T_i]$ are linearly independent in~$\Ksp(\cat)$. Thus~$\lambda_i = 0$ for all~$i \in \{1, \ldots, n\}$. This finishes the proof.
\end{proof}

@@

\begin{corollary}
If~$\ind(\cat)$ is finite, then the set
\[
\set{[\ell_A]}{A \in \ind(\cat) \ssm \add(\susp T)} \cup \set{[\susp T_i]}{i=1, \ldots, n}
\]
is a basis of~$\Ksp(\cat)$.
\end{corollary}

@@

We first recall the results on categorification of cluster algebras that we will make use of in the proofs.
\begin{theorem}[]\pg{cite???}
\label{thm::categorification}
Let~$\cat$ be the cluster category of a valued quiver of Dynkin type~$A,B,C,D,E,F$ or~$G$. Let~$T$ be a basic cluster-tilting object in~$\cat$, and let~$Q$ be the valued Gabriel quiver of~$\End{\cat}(T)$. Then there is a bijection
\[
\CC: \ind(\cat) \xrightarrow{} \{\textrm{cluster variables in the cluster algebra of~$Q$}\},
\]
expressing cluster variables as Laurent polynomials in the variables of the cluster~$\CC(T)$ and which has the follwing properties.
\begin{itemize}
\item[(i)] \emph{(}\cite[Prop.~3.2]{BuanMarshReinekeReitenTodorov} and~\cite[]{???} \emph{)} For any~$X,Y \in \ind(\cat)$, $\CC(X)$ and~$\CC(Y)$ are compatible if and only if~$\cat(X, \susp Y) = 0$.
\item[(ii)] \emph{(}\cite[Prop.~4.3]{FuKeller} and \emph{)} For any~$X \in \ind(\cat)$, the~$\b{g}$-vector of~$\CC(X)$ is~$\b{g}([X])$, where we identify~$\Z^n$ and~$K_0(\cat ; T)$ via the isomorphism sending~$(a_1, \ldots, a_n)$ to~$\sum_{i=1}^n a_i [T_i]$.
\item[(iii)] \emph{(}\cite[Thm.~7.5]{BuanMarshReinekeReitenTodorov} and~\cite[]{???—} \emph{)} For any~$X,Y \in \ind(\cat)$, $\CC(X)$ and~$\CC(Y)$ are exchangeable if and only if~$\dim_{\field_X}\cat(X, \susp Y) = \dim_{\field_Y}\cat(X, \susp Y) = 1$.
\item[(iv)]\emph{(}\cite[???]{BuanMarshReinekeReitenTodorov} and~\cite[???]{BuanIyamaReitenScott} and ???\emph{)} Let~$T'$ be any basic cluster-tilting object of~$\cat$. Then the matrix~$B'$ of the associated seed~$(\CC(T'),B')$ is given by the multiplicities of the middle terms of the exchange triangles. More explicitely,
\end{itemize}
\end{theorem}

>>>>

\begin{proposition}
\label{prop::free-set}
\begin{enumerate}
\item The set~$\set{[\ell_A]}{A \in \ind(\cat) \ssm \add(\susp T)} \cup \set{[\susp T_i]}{i \in [n]}$ is free in~$\Ksp(\cat)$.
\item The set~$\set{[r_A]}{A \in \ind(\cat) \ssm \add(\susp T)} \cup \set{[\susp T_i]}{i \in [n]}$ is free in~$\Ksp(\cat)$.
\end{enumerate}
\end{proposition}

\begin{proof}
We only prove (1); the proof of (2) is similar. Assume that~
\[
x= \sum_{A \in \ind(\cat) \ssm \add(\susp T)} \lambda_A \ell_A + \sum_{i=1}^n \lambda_i [\susp T_i] = 0.
\]
Then~$\langle x, [A] \rangle = 0$ for all~$A\in\ind(\cat) \ssm \add(\susp T)$. But~$\langle x, [A] \rangle = \lambda_A$ by \cref{lemm::bilinear-form}. Thus~
\[
x = \sum_{i=1}^n \lambda_i [\susp T_i] = 0.
\]
But the~$[\susp T_i]$ are linearly independent in~$\Ksp(\cat)$. Thus~$\lambda_i = 0$ for all~$i \in [n]$. This finishes the proof.
\end{proof}

@@

\begin{corollary}
If~$\ind(\cat)$ is finite, then the set
\[
\set{[\ell_A]}{A \in \ind(\cat) \ssm \add(\susp T)} \cup \set{[\susp T_i]}{i \in [n]}
\]
is a basis of~$\Ksp(\cat)$.
\end{corollary}

@@

We first recall the results on categorification of cluster algebras that we will make use of in the proofs.
\begin{theorem}[]\pg{cite???}
\label{thm::categorification}
Let~$\cat$ be the cluster category of a valued quiver of Dynkin type~$A,B,C,D,E,F$ or~$G$. Let~$T$ be a basic cluster-tilting object in~$\cat$, and let~$Q$ be the valued Gabriel quiver of~$\End{\cat}(T)$. Then there is a bijection
\[
\CC: \ind(\cat) \xrightarrow{} \{\textrm{cluster variables in the cluster algebra of~$Q$}\},
\]
expressing cluster variables as Laurent polynomials in the variables of the cluster~$\CC(T)$ and which has the follwing properties.
\begin{itemize}
\item[(i)] \emph{(}\cite[Prop.~3.2]{BuanMarshReinekeReitenTodorov} and~\cite[]{???} \emph{)} For any~$X,Y \in \ind(\cat)$, $\CC(X)$ and~$\CC(Y)$ are compatible if and only if~$\cat(X, \susp Y) = 0$.
\item[(ii)] \emph{(}\cite[Prop.~4.3]{FuKeller} and \emph{)} For any~$X \in \ind(\cat)$, the~$\b{g}$-vector of~$\CC(X)$ is~$\b{g}([X])$, where we identify~$\Z^n$ and~$K_0(\cat ; T)$ via the isomorphism sending~$(a_1, \dots, a_n)$ to~$\sum_{i=1}^n a_i [T_i]$.
\item[(iii)] \emph{(}\cite[Thm.~7.5]{BuanMarshReinekeReitenTodorov} and~\cite[]{???—} \emph{)} For any~$X,Y \in \ind(\cat)$, $\CC(X)$ and~$\CC(Y)$ are exchangeable if and only if~$\dim_{\field_X}\cat(X, \susp Y) = \dim_{\field_Y}\cat(X, \susp Y) = 1$.
\item[(iv)]\emph{(}\cite[???]{BuanMarshReinekeReitenTodorov} and~\cite[???]{BuanIyamaReitenScott} and ???\emph{)} Let~$T'$ be any basic cluster-tilting object of~$\cat$. Then the matrix~$B'$ of the associated seed~$(\CC(T'),B')$ is given by the multiplicities of the middle terms of the exchange triangles. More explicitely,
\end{itemize}
\end{theorem}
